[dcpo_demsupport]

### 2020-07-06 paper/dcpo_demsupport.Rmd
add data/dcpo_theta.rda and data/dcpo_y_r_pred.rda

>>>>

```{r dcpo, eval=FALSE}
iter <- 3000

dcpo_output <- dcpo(dcpo_input,
                    iter = iter,
                    chains = 4,
                    thin = iter/500, # this yields 250 draws per chain, 1000 draws total
                    pars = c("sd_delta","sd_theta_evolve", "sd_sigma_evolve", "sigma","phi","beta","alpha","delta","theta","y_r_pred","log_lik"))

save(dcpo_output, file = here::here("data", "dcpo_output.rda"))

dcpo_theta <- rstan::extract(dcpo_output, pars = "theta")

save(dcpo_theta, file = here::here("data", "dcpo_theta.rda"))

dcpo_y_r_pred <- rstan::extract(dcpo_output, pars = "y_r_pred")

save(dcpo_input, dcpo_x_pred, file = here::here("data", "dcpo_y_r_pred.rda"))
```
